---
title: "Analysis of PGY1 Interviews for 2017-2018"
author: "Brian Gulbis"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: default
  html_document:
    code_folding: hide
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

```{r data, message=FALSE}
library(tidyverse)
library(readxl)
library(stringr)
library(forcats)
library(pander)
panderOptions('table.alignment.default', 'left')
panderOptions('table.split.table', Inf)

survey <- read_excel("../data/raw/2017_survey_responses.xlsx") %>%
    dmap_at(c("OriginalResponse", "ShortAnswer"), na_if, y = "NA")
ratings <- read_excel("../data/raw/2017_interview_interactions.xlsx")

mh_ranking <- survey %>%
    filter(Question == 5) %>%
    dmap_at("ShortAnswer", ~ factor(.x, levels = c("First Choice", "Second Choice", "Third Choice or Below", "Did Not Rank"), ordered = TRUE))
```

```{r theme}
theme_bg <- function(base_size = 11, base_family = "") {
    theme_bw(base_family = base_family, base_size = base_size) +
        theme(legend.background = element_blank(),
              legend.key = element_blank(),
              legend.text = element_text(color = "grey35"),
              panel.background = element_blank(),
              panel.border = element_blank(),
              strip.background = element_blank(),
              strip.text = element_text(color = "grey35"),
              plot.background = element_blank(),
              panel.grid = element_blank(),
              axis.line = element_line(color = "grey85"),
              axis.text = element_text(color = "grey35"),
              axis.title = element_text(color = "grey35"),
              axis.ticks = element_line(color = "grey35"))
}
```

## How candidates ranked our program

```{r, fig.cap="Where Respondants Ranked Us"}
ggplot(mh_ranking, aes(x = ShortAnswer)) +
    geom_bar() +
    xlab("") +
    ylab("Number of Responses") +
    theme_bg()
```

## Reasons why we were not first choice

```{r, results='asis'}
x <- survey %>%
    filter(Question == 6, !is.na(OriginalResponse)) %>%
    select(-ShortAnswer) %>%
    left_join(mh_ranking[c("Responder", "ShortAnswer")], by = "Responder") %>%
    select(Rating = ShortAnswer, Comments = OriginalResponse) %>%
    group_by(Rating) %>%
    by_slice(map, as.list, .to = "Comments") 

y <- flatten(x) %>%
    flatten()
y <- y[4:6]
names(y) <- x$Rating
pander(y)
```

## Ratings for each component of your interview day

```{r, fig.width=8, fig.cap="How Respondants Rated Each Portion of Interview Day"}
ratings %>%
    dmap_at("Score", ~ factor(.x, levels = c("Excellent", "Above Average", "Average", "Below Average"), ordered = TRUE)) %>%
    ggplot(aes(x = Score)) +
    geom_bar() +
    xlab("Rating") +
    ylab("Number of Responses") +
    facet_wrap(~ Attribute) +
    coord_flip() +
    theme_bg()
```

```{r, eval=FALSE, fig.cap="Slope graph of ratings"}
ratings %>%
    dmap_at("Score", ~ factor(.x, levels = c("Excellent", "Above Average", "Average", "Below Average"), ordered = TRUE)) %>%
    dmap_at("Responder", as.character) %>%
    dmap_at("Responder", as_factor) %>%
    ggplot(aes(x = as_factor(Attribute), y = Score, color = Responder)) +
    geom_point() +
    geom_line() +
    xlab("Attribute") +
    ylab("Rating") +
    theme_bg()
```

## Most important factors when deciding what order to rank residency programs

```{r, results='asis'}
x <- survey %>%
    filter(Question == 2, !is.na(OriginalResponse)) %>%
    select(-ShortAnswer) %>%
    left_join(mh_ranking[c("Responder", "ShortAnswer")], by = "Responder") %>%
    select(Rating = ShortAnswer, Comments = OriginalResponse) %>%
    group_by(Rating) %>%
    by_slice(map, as.list, .to = "Comments") 

y <- flatten(x) %>%
    flatten()
y <- y[5:8]
names(y) <- x$Rating
pander(y)
```

## Did the MMI influence the way you ranked our residency program

```{r}
survey %>%
    filter(Question == 4) %>%
    ggplot(aes(x = ShortAnswer)) +
    geom_bar() +
    xlab("") +
    ylab("Number of Respones") +
    coord_flip() +
    theme_bg()
```

## How candidates first learned of our program

```{r}
survey %>%
    filter(Question == 1) %>%
    dmap_at("ShortAnswer", fct_infreq) %>%
    ggplot(aes(x = ShortAnswer)) +
    geom_bar() +
    xlab("") +
    ylab("Number of Respones") +
    coord_flip() +
    theme_bg()
```


## Provide any suggestions to improve the interview process

```{r}
x <- survey %>%
    filter(Question == 7, !is.na(OriginalResponse)) %>%
    select(-ShortAnswer) %>%
    left_join(mh_ranking[c("Responder", "ShortAnswer")], by = "Responder") %>%
    select(Rating = ShortAnswer, Comments = OriginalResponse) %>%
    group_by(Rating) %>%
    by_slice(map, as.list, .to = "Comments") 

y <- flatten(x) %>%
    flatten()
y <- y[5:8]
names(y) <- x$Rating
pander(y)
# knitr::kable(caption = "Suggestions for improving the interview day")
```
